Coastal Flooding (surface water, highway, sewer and watercourse flooding) across Torbay, UK

### 2016-10-19 EU-Circle/eu-circle_case-study-3.Rmd
Update

```{r DS}
## The wet-day frequency and SLP
ds.fw <- DS(subset(eof.fw,pattern=1:4),eof.slp,eofs=1:5)
plot(ds.fw)
ds.mu <- DS(subset(eof.mu,pattern=1:4),eof.es,eofs=1:7)
plot(ds.mu)
```

>>>>

```{r DS}
## The wet-day frequency and SLP
ds.fw <- DS(subset(eof.fw,ip=1:4),eof.slp,eofs=1:5)
plot(ds.fw)
ds.mu <- DS(subset(eof.mu,ip=1:4),eof.es,eofs=1:7)
plot(ds.mu)
```
